Visualizing Conditional Relationships

### 2017-08-30 paper/main.tex
intro pics+bib+table

\section{Introduction}
\label{sec:introduction}
\begin{figure}
  \includegraphics{chart_chooser}
  \caption{From Bertin's Semiology of Graphics \cite{bertin}, this diagram
    illustrates how there are many ways to display the same information about the 1954 Frnech
  workforce.}
  \label{fig:chart_chooser}
\end{figure}

@@

Quite often, it is this disaggregation that is interesting to researchers
because it points to multiple factors that can contribute to the measured
outcome. The difficulty is in figuring out how to visualize this
disaggregation, especially as the data structure grows more complex. Cross
tabulation tables work for a small number of categorical variables, but are
pushed to the limits at n=3 or 4. And most data is not solely categorical,
instead often having quantitative densities of one sort or another. A complex but
important form of quantitative densities are functional densities, where they are drawn from a continuous sample of observations \cite{ramsey2006, ramsey2002, muller2006}. That continuous sample is often over space or time or another parameter or combination thereof, and often it is
important to preserve those functional dependencies in the visualization. For
example, for storm modeling it is important to show the expected time and
location of the rainfall. This survey presents a sampling of visualization
techniques that attempt to illustrate these conditional and functional
relationships within a dataset.

\begin{table}

\begin{tabular}
                & Distribution           & Density 
   Distribution & P(X|Y),P(A,B,C|E,F,G)  & 
   Density      &              & p(X|Y), p(A,B,C|E,F,G)
\end{tabular}

\caption{The rows represent the known distributions & densities while the
  columns are the distributions and densities that the visualization aims to derive.}
\end{table}

While this survey focuses on data structured in a linear, tabular, or
data cube way\cite{munzner data structure}, it could potentially be expanded to network data where the xi
parameters represent edges in the graph.

\subfile{sections/distdist.tex}
\subfile{sections/distdens.tex}
\subfile{sections/densdist.tex}
\subfile{sections/densdens.tex}

>>>>

\section{Introduction}
\label{sec:introduction}
\begin{figure}
  \includegraphics{chart_chooser.png}
  \caption{From Bertin's Semiology of Graphics \cite{bertin_semiology_2011}, this diagram
    illustrates how there are many ways to display the same information about the 1954 Frnech
  workforce.}
  \label{fig:chart_chooser}
\end{figure}

@@

Quite often, it is this disaggregation that is interesting to researchers
because it points to multiple factors that can contribute to the measured
outcome. The difficulty is in figuring out how to visualize this
disaggregation, especially as the data structure grows more complex. Cross
tabulation tables work for a small number of categorical variables, but are
pushed to the limits at n=3 or 4. And most data is not solely categorical,
instead often having quantitative densities of one sort or another. A complex but
important form of quantitative densities are functional densities, where they are drawn from a continuous sample of observations \cite{ramsay_functional_2006, muller_functional_2006}. That continuous sample is often over space or time or another parameter or combination thereof, and often it is
important to preserve those functional dependencies in the visualization. For
example, for storm modeling it is important to show the expected time and
location of the rainfall. This survey presents a sampling of visualization
techniques that attempt to illustrate these conditional and functional
relationships within a dataset.

\begin{table}
\begin{center}
\begin{tabular}{lll}
   Variable Type& Distribution           & Density\\ 
   Distribution & $P(X\|Y),P(A,B,C|E,F,G)$  &  \\
   Density      &                        & $p(X\|Y), p(A,B,C\|E,F,G)$\\
\end{tabular}
\caption{The rows represent the known distributions and densities while the
  columns are the distributions and densities that the visualization aims to derive.}
  \end{center}
\end{table}

While this survey focuses on data structured in a linear, tabular, or
data cube way\cite{munzner_what:_2014}, it could potentially be expanded to network data.

%%\subfile{sections/distdist.tex}
%%\subfile{sections/distdens.tex}
%%\subfile{sections/densdist.tex}
%%\subfile{sections/densdens.tex}

### 2017-08-30 paper/sections/densdens.tex
intro pics+bib+table

>>>>

\begin{figure}
  \includegraphics{partial_dependence}
  \caption{Taken from Scikit Learn\cite{scikit_learn}, the line plots show how California housing prices are partially dependent on each x variable. The heat map illustrates the joint effect of the age the house and the number of occupants in the house.}
  \label{fig:partialdependence}
\end{figure}

One of the most straightforward ways to show dependencies is to plot one
variable against another, but those methods often exclude the effects of the
other variables in the datasets. Regression methods can be used to analyze the
ways in which one variable is partially dependent on many other variables in
the dataset\cite{Hastie_Tibshirani}. As shown in figure~\ref{fig:partialdependence}, one way partial dependence line plots and two way partial dependence heat maps show how California housing prices are marginally dependent on each variable.
